---
title: "Codebook"
output:
  html_document: 
    code_folding: hide
    fig_height: 6
    fig_width: 8
    theme: spacelab
    toc: yes
    toc_depth: 5
    toc_float: yes
    output_dir: "docs"
---

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

```{=html}
<style type="text/css">
.tablelines table, .tablelines td, .tablelines th {
  border: 1px solid black;
  }
.centrado {
  text-align: center;
}
.table.center {
  margin-left:auto; 
  margin-right:auto;
}
.table_wrapper{
  display: block;
  overflow-x: auto;
  white-space: nowrap;
}
code.r{
  font-size: 8px;
}
body{ /* Normal  */
    text-align: justify;
}
.superbigimage{
  overflow-y:scroll;
  white-space: nowrap;
}
.superbigimage img{
  overflow-y: scroll;
  overflow-x: hidden;
}
p.comment {
  background-color: #FF7F79;
    padding: 10px;
  border: 1px solid black;
  margin-left: 25px;
  border-radius: 5px;
  font-style: italic;
}
</style>
```
```{=html}
<style>
  p.comment {
    background-color: #ff9a9a;
      padding: 10px;
    border: 1px solid red;
    margin-left: 25px;
    border-radius: 5px;
    font-style: italic;
  }

</style>
```
```{r setup, include=FALSE}
rm(list=ls());gc()
# xaringan::inf_mr()

      tryCatch(
                     {
      load("C:/Users/andre/Dropbox/Covid-19_2020/Article_SecondManuscript/LT Environmental analysis/Databases/merged_data_proj_post_ago.RData")
                     },
                         error = function(e){
      load(paste0(gsub("codebook.Rmd","",rstudioapi::getSourceEditorContext()$path),"merged_data_proj_post_ago.RData"))
                         }
                   )
sessionInfo()
```

## date: `r format(Sys.time(), '%d %B, %Y')`

```{r codebook_final, echo=T,error=T}
codebook::codebook(codebook_data) #638622
```

# References

-   Hale T, Angrist N, Kira B, et al. (May 25, 2020). Variation in government responses to COVID-19 (version 6.0).Blavatnik School of Government working paper. <https://www.bsg.ox.ac.uk/sites/default/files/2020-05/BSG-WP-2020-032-v6.0.pdf> (accessed July 11, 2020).

-   Hart,E. (). rWBclimate: A package for accessing World Bank climate data. R package version 0.1.3 <http://github.com/ropensci/rWBclimate>

-   Global Burden of Disease Collaborative Network. Global Burden of Disease Study 2017 (GBD 2017) Results. Seattle, United States: Institute for Health Metrics and Evaluation (IHME), 2018. Available from <http://ghdx.healthdata.org/gbd-results-tool>.
